### 2017-10-03 README.Rmd
add preprint citation

> Population structure and phenotypic variation of *Sclerotinia sclerotiorum*
> from dry bean in the United States
>
> Z. N. Kamvar, B. S. Amaradasa, R. Jhala, S. McCoy, J. Steadman, and S. E. Everhart

@@

### Pulling the container

```
docker run --rm -it -v $(pwd):/analysis zkamvar/sclerotinia-366:latest bash
```

### Building the container

@@

```sh
docker build .
```

This will bootstrap the environment to build the container. Once it's finished
you should see:

```
Successfully built 8e1e4cd82e19
```

where `8e1e4cd82e19` will be replaced by your hash. Now that things are built,
you can run the analysis in the image with:

```
docker run -it -v $(pwd):/analysis 8e1e4cd82e19 bash
```

>>>>

# Citation

## Manuscript

> Kamvar ZN, Amaradasa BS, Jhala R, McCoy S, Steadman JR, Everhart SE. (2017) Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States. *PeerJ Preprints* 5:e3311v1 <https://doi.org/10.7287/peerj.preprints.3311v1>

## Data and Code

> Kamvar, Z. N., Amaradasa, B. S., Jhala, R., McCoy, S., Steadman, J., & Everhart, S. E. (2017, October 3). Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States. <http://doi.org/10.17605/OSF.IO/EJB5Y>

@@

### RStudio Server

```
docker run --rm -dp 8787:8787 zkamvar/sclerotinia-366:latest
```

This will spin up the Docker container on your machine and expose it to port 8787. You can open your browser and type `localhost:8787`, and an instance of Rstudio server will appear. Sign in with the username: rstudio and password: rstudio.

Since the files in `/analysis` are write-protected, if you wanted to explore, you should copy the directory to your current working space:

- in the R console type: `system("cp -R /analysis .")`. 
- open `/analysis` and double click on znk_analysis.Rproj

From here you can re-run the analyses to your heart's content.

### Building the container locally

@@

```sh
docker build -t sclerotinia-366 .
```

Now that things are built, you can run the analysis in the image with:

```
docker run -it sclerotinia-366 bash
```
